Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2018-01-16 Thesis/Thesis.rnw
Assorted edits and figure rearrangements

% TODO: DOI in bib?
% TODO: Prettier abstract sectioning
% TODO: Better calendrical cues in plots

@@

<<util>>=
@

\documentclass[10pt,a4paper,draft]{article}

@@

\usepackage{hyperref}
\usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
\usepackage{tikz}
\usepackage{draftwatermark}
\SetWatermarkScale{1}
\SetWatermarkAngle{45}
\SetWatermarkFontSize{4ex}
\SetWatermarkHorCenter{12ex}
\SetWatermarkVerCenter{12ex}
\SetWatermarkLightness{.5}
\SetWatermarkText{DRAFT 2}

@@

\usepackage{hanging}

@@

\title{Optimization of respiratory syncytial virus prophylaxis using a generalized additive model of Connecticut hospitalizations}
\def\headertitle{Optimization of RSV prophylaxis using a generalized additive model of Connecticut hospitalizations}

@@

\maketitle
\thispagestyle{firstpage}

@@

\subsection{Spatio-temporal variability of RSV in Connecticut}

The Department of Public Health of the state of Connecticut, via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state. Previous analysis of this database has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188}

@@

\begin{itemize}
	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
	\item Can we use spatial analysis of RSV to propose alternate regimens, either statewide or regional, that would improve effectiveness over AAP-recommended prophylaxis, without increasing treatment cost?
	\item Is there year-to-year variation in timing of RSV season in Connecticut?
	\item Can we take advantage of any year-to-year variation to improve upon AAP-recommended prophylaxis, without increasing treatment cost?
\end{itemize}

@@

We identified \Sexpr{nrow(dataset)} cases of RSV in Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)}.

@@

@@

Our goal was to construct a model of RSV incidence over time that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset, or preventable RSV case fraction.

@@

We were willing to assume that RSV incidence can be modeled as a twice-differentiable piecewise Poisson time series.

@@

We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks (as long as the outbreaks are amenable to GAM); this package is available at \href{https://github.com/airbornemint/outbreakpredict}{\nolinkurl{github.com/airbornemint/outbreakpredict}}.

@@

For our spatial analysis, we aggregated RSV incidence data across all years in our data set. We then spatially aggregated the data to form five regions:

% TODO: map

\begin{itemize}
    \item One region for the entire state
    \item One region for each of the counties with high incidence of RSV: Hartford County, Fairfield County, and New Haven County.
    \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))}
\end{itemize}

@@

We chose to aggregate low-incidence counties into a single region because our analysis in those counties individually would have yielded results with unacceptably low statistical power.

@@

The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternate prophylaxis regimens (as described below), while maintaining 6-month dosing schedule (and therefore not increasing medication cost). Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced suboptimal results.

\subsection{Devising alternate all-years prophylaxis regimens}

Following this analysis, we devised six alternate spatially adjusted prophylaxis regimens. In all our alternate regimens, prophylaxis consists of six monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.

\begin{itemize}
    \item \textbf{By statewide all-years onset}: prophylaxis administration begins at statewide all-years median RSV season onset. 
    \item \textbf{By statewide all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide all-years median) season onset and offset. 
    \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the (statewide all-years median) RSV season offset. 
    \item \textbf{By regional all-years onset}: prophylaxis administration begins at regional\footnote{county-wide, or --- in the case of low-incidence counties --- low-incidence-region-wide} all-years median RSV season onset.
    \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (regional all-years median) RSV season onset and offset. 
    \item \textbf{By regional all-years offset}: prophylaxis administration begins 24 weeks before the (regional all-years median) RSV season offset. 
\end{itemize}

\subsection{Evaluating alternate prophylaxis regimens}

We evaluated each of those alternate regimens in the same way we evaluated the current AAP guidelines, as described above.

For the three alternate regimens based on statewide data, we estimated preventable fraction statewide, as well as in each region.

For the three alternate regimens based on regional data, we estimated preventable fraction in the corresponding region.

@@

\begin{itemize}
    \item \textbf{Weekly rounding}: prophylaxis start and end date rounded to the nearest calendar week,
    \item \textbf{Biweekly rounding}: prophylaxis start and end date rounded to the nearest two-week calendar period, with two-week period boundary chosen , and % TODO: specifics
    \item \textbf{Monthly rounding}: prophylaxis start and end date rounded to the nearest four-week calendar period.  % TODO: specifics and also not actually in code now
\end{itemize}

@@

\subsection{Estimating characteristics of RSV surseasons}

@@

\subsection{Evaluating temporal variation of RSV seasonality}

@@

\subsection{Devising alternate recent-years prophylaxis regimens}

Finally, to assess the impact of any long-term trends in RSV season timing on prophylaxis, we formulated three additional prophylaxis regimens. Here, each prophylaxis regimen is adjusted annually based on RSV data from the preceding surseason:

@@

As before, these alternate regimens involved six monthly doses of palivizumab giving 24 weeks of protection.

@@

\setcounter{figure}{1}
\begin{figure*}
<<coverageByRegionAAPInsight, results='hide'>>=
    tikz(sprintf("%s/coverageByRegionAAPInsight.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight, pointsize=10)

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) +
    	geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), linetype="11", data=spans) + 
    	geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), linetype="11", data=spans) + 
    	geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans) + 
    	geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype=3, data=thresholds) + 
        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype=3, data=thresholds) + 
        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0)) +
        scale_color_manual(labels=spanLabels, values=twoTone) +
        scale_fill_manual(labels=spanLabels, values=twoTone) +
        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
        facet_wrap(~county, ncol=5) +
        labs(x="Surveillance week") + 
        theme(
            legend.title=element_blank(),
            axis.title.y=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )

    dev.off()
@
\input{\figuresDir/coverageByRegionAAPInsight.tex}
\caption{Weekly RSV relative cumulative incidence in Connecticut, by region}
\label{fig:coverageByRegionAAPInsight}
\end{figure*}
\setcounter{figure}{0}

\paragraph{RSV season in Fairfield county begins early and ends late}

\paragraph{RSV season in low-incidence counties begins late}

Meanwhile, in comparison with the statewide RSV season onset and offset, the low-incidence region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median. (Figure \ref{fig:seasonByRegion}.)

\begin{figure}
<<seasonByRegion, results='hide'>>=
    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    data = thresholdsByCounty %>% 
        filter(county %in% countiesForPlots) %>%
        melt(id=c("county")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
        cast(county + variable ~ pctile)

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
        geom_point(aes(y=median, x=county)) + 
        labs(aes(x=variable)) +
        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
        scale_x_discrete(labels=countyLabels) + 
        labs(y="Surveillance week") + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            axis.text.x=element_text(angle=30, hjust=1)
        )
    dev.off()
@
\begin{center}
\input{\figuresDir/seasonByRegion.tex}
\caption{RSV season onset and offset in Connecticut, by region}
\label{fig:seasonByRegion}
\end{center}
\end{figure}
\setcounter{figure}{2}

\paragraph{AAP guidelines perform best in low-incidence counties and worst in Fairfield county}

Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered according to AAP guidelines, offers protection.

The AAP guidelines perform better in the low-incidence counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time. (Figure \ref{fig:coverageByRegionAAP}.)

\begin{figure}
<<coverageByRegionAAP, results='hide'>>=
    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.1) + 
        geom_point(aes(y=frac.median, x=county)) + 
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_x_discrete(labels=countyLabels) + 
        labs(y="Preventable fraction") +
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            axis.text.x=element_text(angle=30, hjust=1)
        )
    dev.off()
@
\input{\figuresDir/coverageByRegionAAP.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to AAP guidelines, by region}
\label{fig:coverageByRegionAAP}
\end{figure}

The cause of this is evident in figure \ref{fig:coverageByRegionAAPInsight}, showing temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of the AAP-recommended prophylaxis regimen. Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.

\paragraph{Spatially-informed regimens are superior to AAP recommendations overall and in Hartford county}

@@

Statewide, the AAP guidelines offer protection for \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}); meanwhile, the regimens based on all-years statewide onset produce the weakest improvement at \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} coverage (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}), and other alternate regimens yield similar results.

In Hartford county, the improvement is similar. Here, the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}); the regimens based on all-years regional offset generate the weakest improvement to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} protection (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}), and other alternate regimens are comparable.

@@

\begin{figure*}
<<coverageByRegion, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE)

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        scale_x_discrete(labels=countyLabels) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@
\input{\figuresDir/coverageByRegionRegimen.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
\label{fig:coverageByRegionRegimen}
\end{figure*}

@@

\begin{figure*}
<<coverageByRounding, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)

@@

>>>>

% TODO: Better calendrical cues in plots, maybe also with bars?
% TODO: establish need in intro
% TODO: adverse effects of immunoprophylaxis

@@

<<util, warning=FALSE>>=
@

\documentclass[10pt,a4paper]{article}

@@

\usepackage{hyperref}
\usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
\usepackage{tikz}
\usepackage{draftwatermark}
\SetWatermarkScale{1}
\SetWatermarkAngle{45}
\SetWatermarkFontSize{4ex}
\SetWatermarkHorCenter{12ex}
\SetWatermarkVerCenter{12ex}
\SetWatermarkLightness{.5}
\SetWatermarkText{DRAFT 3}

@@

\usepackage{hanging}
\usepackage{graphicx}

@@

\title{Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
\def\headertitle{Assessment and optimization of RSV prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}

@@

\maketitle

\begin{center}

\vspace{20pt}
\large Submitted to the School of Public Health and the School of Medicine, in partial fulfillment of the requirements for the degrees of Master of Public Health and Master of Medical Sciences

\vspace{40pt}

\includegraphics[height=2.5in]{EPH}
\hspace{40pt}
\includegraphics[height=2.5in]{Medicine}

\end{center}

\thispagestyle{firstpage}

@@

\subsection{Spatio-temporal variability of RSV}

Nationwide spatial variability of RSV season has been established by the Centers for Disease Control and Prevention (CDC).\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}

The Department of Public Health of the state of Connecticut (CT DPH), via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state. Previous analysis of this database at the Yale University School of Public Health has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188}

@@

\begin{itemize}
	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
	\item Can we use spatial analysis of RSV to propose alternate regimens, either statewide or regional, that would regionally improve effectiveness over AAP-recommended prophylaxis, without increasing the total cost of the prophylactics the regimen?
	\item Is there year-to-year variation in timing of RSV season in Connecticut?
	\item Can we take advantage of any year-to-year variation to improve upon AAP-recommended prophylaxis, without increasing treatment cost?
\end{itemize}

@@

We identified \Sexpr{nrow(dataset)} hospitalization coded as RSV in Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)}.

@@

The study was approved by the Human Investigation Committees at Yale University and the CT DPH. The authors assume full responsibility for analyses and interpretation of the data obtained from CT DPH.

@@

Our goal was to construct a model of annual RSV incidence that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset, or preventable RSV case fraction.

@@

We were willing to assume that RSV incidence is the result of a Poisson process whose log can be modeled as a piecewise twice-differentiable function of time.

@@

We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks (as long as the outbreaks are amenable to GAM); this package is available at \href{https://github.com/airbornemint/outbreak-predict}{\nolinkurl{github.com/airbornemint/outbreak-predict}}.

\begin{figure}
\begin{center}
\input{\figuresDir/map.tex}
\caption{RSV case burden in Connecticut counties}
\label{fig:map}
\end{center}
\end{figure}

@@

<<map, results='hide'>>=
    tikz(sprintf("%s/map.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    US.counties = readOGR(dsn="../Maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
    US.counties = US.counties[US.counties$STATEFP == "09",]
    county.data = US.counties@data %>%
        mutate(id=rownames(.)) %>%
        data.table() %>%
        mutate(highRSV=ifelse(NAME %in% lowIncidenceCounties, FALSE, TRUE))

    map.df = US.counties %>% 
        fortify() %>% 
        data.table() %>%
        inner_join(county.data %>% select(highRSV, id), by="id")

    county.data = map.df %>%
        group_by(id) %>%
        summarize(lat=mean(range(lat)), long=mean(range(long))) %>%
        ungroup() %>%
        inner_join(county.data, by="id") %>%
        rename(name=NAME)

    ggplot(map.df, aes(x=long, y=lat)) +
        theme_light(base_size=plotTextBaseSize) +
        scale_fill_manual(labels=legendLabels(c("$<$50", "$>$100")), values=twoTone) +
        geom_polygon(aes(fill=highRSV, group=group), color="white", size=.5) +
        geom_text(data=county.data, aes(label=name), size=2.2) +
        coord_map() + 
        labs(fill="Average RSV cases per year") +
        theme(
            rect=element_blank(),
            line=element_blank(),
            axis.text=element_blank(),
            axis.title=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@

For our spatial analysis, we aggregated RSV incidence data across all years in our data set. We then spatially aggregated the data to form five regions (Figure \ref{fig:map}):

\begin{itemize}
    \item One region for the entire state
    \item One region for each of the counties with high case counts of RSV: Hartford County, Fairfield County, and New Haven County.
    \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-RSV counties'')
\end{itemize}

@@

We chose to aggregate low-RSV counties into a single region because our analysis in those counties individually would have yielded results with unacceptably low statistical power.

@@

The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternate prophylaxis regimens (as described below), while maintaining 6-month dosing schedule (and therefore not increasing medication cost). Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced prophylaxis regimens starting weeks prior to RSV season onset or ending weeks after RSV season offset.

\subsection{Evaluating alternate all-years prophylaxis regimens}

Following this analysis, we estimated the regional and statewide preventable fraction for six alternate spatially adjusted prophylaxis regimens:

\begin{itemize}
    \item \textbf{By statewide all-years onset}: prophylaxis administration begins at statewide all-years median RSV season onset. 
    \item \textbf{By statewide all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide all-years median) season onset and offset. 
    \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the (statewide all-years median) RSV season offset. 
    \item \textbf{By regional all-years onset}: prophylaxis administration begins at regional\footnote{county-wide, or --- in the case of low-RSV counties --- low-RSV-region-wide} all-years median RSV season onset.
    \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (regional all-years median) RSV season onset and offset. 
    \item \textbf{By regional all-years offset}: prophylaxis administration begins 24 weeks before the (regional all-years median) RSV season offset. 
\end{itemize}

In all our alternate regimens, prophylaxis consists of five monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.

@@

\begin{itemize}
    \item \textbf{Weekly rounding}: prophylaxis start and end date rounded to the nearest calendar week,
    \item \textbf{Biweekly rounding}: prophylaxis start and end date rounded to the nearest two-week calendar period, with periods chosen to approximately align with November 15th, and
    \item \textbf{Monthly rounding}: prophylaxis start and end date rounded to the nearest four-week calendar periods, with periods chosen to approximately align with November 15th.
\end{itemize}

@@

@@

@@

\subsection{Evaluating alternate recent-years prophylaxis regimens}

Finally, to assess the impact of any long-term trends in RSV season timing on prophylaxis, we evaluated three additional prophylaxis regimens. Here, each prophylaxis regimen is adjusted annually based on RSV data from the preceding surseason:

@@

As before, these alternate regimens involved five monthly doses of palivizumab giving 24 weeks of protection.

\begin{figure*}[b]
\begin{center}
\input{\figuresDir/coverageByRegionAAPInsight.tex}
\caption{RSV relative cumulative incidence in Connecticut, by region}
\label{fig:coverageByRegionAAPInsight}
\end{center}
\end{figure*}

@@

\paragraph{RSV season timing varies regionally}

<<seasonByRegion, results='hide'>>=
    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    data = thresholdsByCounty %>% 
        filter(county %in% countiesForPlots) %>%
        melt(id=c("county")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
        cast(county + variable ~ pctile)

    onsetOffsetRange = 6 # weeks
    onsetOffsetAdjust = data.frame(variable=c("onset", "offset"), nudge=c(-1, -2))

    limits = data %>% 
        select(variable, median) %>%
        group_by(variable) %>%
        summarize(mid=round(mean(range(median)))) %>%
        inner_join(onsetOffsetAdjust, by="variable") %>%
        mutate(mid=mid + nudge, min=mid - onsetOffsetRange / 2, max=mid + onsetOffsetRange / 2)

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
        geom_point(aes(y=median, x=county)) + 
        geom_blank(data=limits, aes(y=min)) + 
        geom_blank(data=limits, aes(y=max)) + 
        labs(aes(x=variable)) +
        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
        scale_x_discrete(labels=countyLabels) + 
        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=epiWeekLabels) + 
        labs(y=NULL) + 
        theme(
            panel.grid.major.y=element_blank(),
            panel.grid.minor.y=element_line(size=rel(2)),
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            axis.ticks.y=element_blank(),
            axis.text.x=element_text(angle=30, hjust=1)
        )
    dev.off()
@

Meanwhile, in comparison with the statewide RSV season onset and offset, the low-RSV region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median. (Figure \ref{fig:seasonByRegion}.)

\begin{figure}
\begin{center}
\input{\figuresDir/seasonByRegion.tex}
\caption{RSV season onset and offset in Connecticut, by region}
\label{fig:seasonByRegion}
\end{center}
\end{figure}

\paragraph{The AAP guidelines perform best in low-RSV counties and worst in Fairfield county}

<<coverageByRegionAAP, results='hide'>>=
    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.1) + 
        geom_point(aes(y=frac.median, x=county)) + 
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_x_discrete(labels=countyLabels) + 
        labs(y="Preventable fraction") +
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            axis.text.x=element_text(angle=30, hjust=1)
        )
    dev.off()
@

<<coverageByRegionAAPInsight, results='hide'>>=
    tikz(sprintf("%s/coverageByRegionAAPInsight.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight, pointsize=10)

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) +
    	geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), linetype="11", data=spans) + 
    	geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), linetype="11", data=spans) + 
    	geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans) + 
    	geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype=3, data=thresholds) + 
        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype=3, data=thresholds) + 
        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0)) +
        scale_x_continuous(breaks=epiWeekBreaks, labels=epiWeekLabels, limits=c(1, 52)) + 
        scale_color_manual(labels=spanLabels, values=twoTone) +
        scale_fill_manual(labels=spanLabels, values=twoTone) +
        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
        facet_wrap(~county, ncol=5, labeller=labeller(county=countyLabels)) +
        labs(x=NULL) + 
        theme(
            panel.grid.major.x=element_blank(),
            panel.grid.minor.x=element_blank(),
            legend.title=element_blank(),
            axis.title.y=element_blank(),
            axis.ticks.x=element_blank(),
            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
            legend.position="bottom"
        )

    dev.off()
@

Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered according to the AAP guidelines, offers protection.

The AAP guidelines perform better in the low-RSV counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time. (Figure \ref{fig:coverageByRegionAAP}.)

The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, showing temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of the AAP-recommended prophylaxis regimen. Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.

\begin{figure}
\begin{center}
\input{\figuresDir/coverageByRegionAAP.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to the AAP guidelines, by region}
\label{fig:coverageByRegionAAP}
\end{center}
\end{figure}

\paragraph{Spatially-adjusted regimens are superior to the AAP recommendations}

<<coverageByRegion, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE)

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        scale_x_discrete(labels=countyLabels) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@

% TODO: Dan says state next paragraph more clearly, it's important

\begin{figure*}
\input{\figuresDir/coverageByRegionRegimen.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
\label{fig:coverageByRegionRegimen}
\end{figure*}

@@

Statewide, the AAP guidelines offer protection for \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}). The regimen based on all-years statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternate regimens yield similar results.

Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}). The regimen based on all-years regional offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternate regimens are comparable.

\begin{figure*}
\begin{center}
\input{\figuresDir/coverageByRoundingRegimen.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by calendrical rounding of prophylaxis regimen}
\label{fig:coverageByRoundingRegimen}
\end{center}
\end{figure*}

\begin{figure*}[!b]
\begin{center}
\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
\label{fig:coverageByRegionRegimenWithSliding}
\end{center}
\end{figure*}

@@

@@

<<coverageByRounding, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)

@@

<<onsetOffsetByYear, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    data = stateThresholdsByWindow %>% 
        melt(id=c("epiyear")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
        cast(epiyear + variable ~ pctile)

    onsetOffsetAdjust = data.frame(variable=c("onset", "offset"), nudge=c(0, -1))
